---
title: "WLui"
author: "Daniel Eaton"
date: "1/14/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Define UI for application that draws a lineplot

```{r}
shinyUI(dashboardPage(
    skin = "white",
    
    # Application title
    dashboardHeader(title = "WellLearner Explorer"),
```

    # Sidebar
    dashboardSidebar(
        
        # Create a selector input for the statistic
        selectInput(
            "stat",
            h4("Choose your desired statistic:"),
            choices = ,
            selected = ...[]
        ),
        
         Create a selector for raw #s or %s
        selectInput(
            'num_or_pct',
            h4('Compare by raw #s or %s:'),
            choices = c("" = "yValue",
                        "" = ""),
            selected = "Raw Numbers"
        ),
        
        # To update the data in the future:
        #fileInput(
            #'file',
            #h4('Upload your csv file:'),
            #accept = '.csv'
        )
    ),
  

# Body
dashboardBody(
    tags$head(
        tags$link(rel = "stylesheet", type = "text/css", href = "custom.css")
    ),
    tabsetPanel(
        tabPanel("Line Graph",
            # Create boxes to style each plot
            fluidRow(
                # Left plot with the line graph for the dataset
                column(width = 6,
                       box(width = NULL,
                           plotOutput("linegraph")
                        )
                )
            )
        )
    )
)
